COG-ED Manuscript

### 2021-11-26 06_Paper/COG-ED/Manuscript.Rmd
adapted formalities and added some sentences

---
title             : "When easy is not preferred: A paradigm for estimating subjective values of cognitive tasks"

author: 
  - name          : "Josephine Zerna"
    affiliation   : "1,*"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    affiliation   : "1,*"
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing

affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden"
  - id            : "*"
    note          : "Shared first authorship"

abstract: |
  Every day, individuals have to weigh the value of the reward when reaching a goal against the required effort.
  However, effort is not inherently aversive to all individuals, which has often been neglected by previous approaches to quantify the subjective value of effort.
  One of them is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013), which can quantify the subjective values of the difficult levels of the n-back task against the easiest level.
  We argue that adapting the paradigm and the method of computing the willingness to exert effort allows two crucial things: Quantifying subjective values without assuming that the easiest level is preferred, and quantifying subjective values for tasks with no objective order of task load.
  We aim to replicate the analysis of Westbrook et al. (2013) with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm (CERED).

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "X"

bibliography      : ref_COG-ED.bib

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf

csl               : apa.csl # this is a workaround for a current bug in the papaja/Rmd software, which fails to shorten multiple authors to "et al."

header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
---

@@

In everyday life, effort and reward are closely intertwined [@Botvinick2009].
With each decision a person makes, they have to evaluate whether the effort required to reach a goal is worth being exerted, given the reward they receive when reaching the goal.
A reward is subjectively more valuable if it is obtained with less effort, so the required effort is used as a reference point for estimating the reward value [@Botvinick2009].
However, the cost of the effort itself is also subjective, and research has not yet established which function best describes the relationship between effort and cost [@Kool2018].
Investigating effort and cost is challenging because “effort is not a property of the target task alone, but also a function of the individual’s cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual’s reward sensitivity” [@Kool2018, p. 209].

## Effort discounting and Need for Cognition 
The individual degree of ED in the study by Westbrook et al. [-@Westbrook2013] was also associated with the participants' Need for Cognition (NFC) score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
Westbrook et al. [-@Westbrook2013] conceptualized NFC as a subjective self-report of ED for each participant which could then be related to the SVs as an objective measure.
On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
Additionally, it has been shown that individuals avoid cognitive effort only to a certain degree, possibly to retain a sense of self-control [@Wu2021], a trait more prominent in individuals with high NFC [@Bertrams2012; @Nishiguchi2016; Xu2021].
However, the relation of NFC and SVs might be confounded, since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance [@Kramer2021] or found no association of NFC and SVs at all [@Crawford2021].
On the other hand, task load has been shown to be a better predictor of SVs than task performance [@Culbreth2016; @Westbrook2013; @Westbrook2019], so more research is needed to shed light on this issue.

## Revising the COG-ED paradigm
The present study changes one fundamental assumption of the original COG-ED paradigm: That the easiest n-back level has the highest SV.
We adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different n-back levels without presuming that all individuals inherently prefer the easiest level.
Figure 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
The COG-ED paradigm sets the SV of 1-back to 1, regardless of the response pattern.
Adding an ED round comparing 2-back and 3-back allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
Adding three ED rounds comparing the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
First, the SVs are still distorted by the SVs returned by the original paradigm, and second, having more task levels would lead to an exponential increase in comparisons.
Therefore, the solution lies in reducing the number of comparisons by presenting an ED round for each possible pair of levels, and by starting each round with a choice between equal prices.
For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
The level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
The level that was not chosen will be set to a fixed value of 2€.
This procedure allows to compute SVs based on actual individual preference instead of objective task load.
Each level's SV is calculated as the mean of this level's SVs from all comparisons in which it appeared.
If the participant has a clear preference for one level, this level's SV will be 1.
If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's ED behaviour can still be quantified.
Since we aim to establish this paradigm for the assessment of tasks with no objective task load, e.g. emotion regulation tasks, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
Additionally, we will compare the ED behaviour of participants regarding the n-back task and an emotion regulation task, the full results of the latter will be published in a second Registered Report.
The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for emotion regulation.

## Hypotheses
Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
Regarding the associations of subjective and objective task load we hypothesized that (1a) performance measured by signal detection *d'* declines with increasing n-back level, (1b) performance measured by reaction time declines with increasing n-back level, and (1c) perceived task load increases with n-back level.
Regarding the associations of task load and ED we hypothesized that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
And regarding individual differences in ED we hypothesized that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.

@@

@@

The paradigm was written and presented using Psychopy [@Peirce2019].
We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
The R Markdown file used to analyze the data and write this document is freely available at github.com/ChScheffel/CERED.
The data can be downloaded from osf.io/vnj8x/.

## Questionnaires
To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
NFC will be assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
Responses to each item (e.g., "Thinking is not my idea of fun", recoded) will be recorded on a 7-point Likert scale.
The NFC scale shows comparably high internal consistency [Cronbach’s $\alpha$ > .80; @Bless1994; @Fleischhauer2010].
Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session.
A full list of measures can be found at osf.io/vnj8x/.

```{r import_image, out.width="50%", warning=FALSE}

  knitr::include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))

## Procedure
Healthy participants aged 18 to 30 years will be recruited using the software *ORSEE* [@Greiner2015].
Participants fill out the personality questionnaires online and then visit the lab for two sessions one week apart.
In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm.
The paradigm starts with the n-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
After each level, participants fill out the NASA-TLX on a tablet.
Then, they complete the ED procedure on screen, where each possible pairing of the four n-back levels is presented in a randomized order.
Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of n-back.
This is done to incentivise truthful behavior in the ED procedure, the n-back data of this part is not analyzed.
The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
The paradigm follows the same structure of task and ED procedure, but participants can decide which strategy they want to reapply in the last block.
Participants receive 30€ in total or course credit for participation.
Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
The sample of the pilot study consisted of $N=$ `r length(datalist_ED)` participants (`r round((table(data_quest$gender)[2]/length(datalist_ED))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).

## Analysis
We aim to conduct all analysis as described in Westbrook et al. [-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
The performance measure *d'* is computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
Reaction time (RT) data is trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes cannot be completed before [@Whelan2008; @Berger2021].
Error- and post-error trials are excluded, because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
Declining performance is investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another rmANOVA with three paired contrasts was computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs are computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
For each ED round, SVs are calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
Then, the final monetary values are divided by 2€, and the SV of each level per participant is computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
A rmANOVA with six paired contrasts is computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Tukey method is used for the paired contrasts of each rmANOVA, including *p*-value adjustment.

To determine the influence of task performance in the association of SVs and n-back level, we will set up a multi-level model.
**MLM explanation goes here**
To ensure the validity of the multi-level model, we conduct a specification curve analysis [@Simonsohn2020], which includes 92 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, $2 SD$ from the mean, $3 SD$ from the mean, RTs below 200 ms), whether post-error trials were excluded or not, and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
The multi-level model will be run with each of the 92 pipelines, which also includes our main pipeline (untransformed data, exclusion of RTs below 200 ms, removal of post-error trials).
The ratio of pipelines that lead to significant versus non-significant effects provides an indication of how robust the effect actually is.

The association of ED and NFC is examined with a regression using the AUC of each participant's SVs to predict their NFC score.
A second regression additionally includes the mean of the NASA-TLX subscales' AUCs of each participant as a predictor.
Since we do not have a fixed SV of 1 for 1-back, we cannot apply the 'AUC' computation of Westbrook et al. [-@Westbrook2013], which was the mean of the AUCs of the SVs of each higher n-back level and 1-back, yielding values between 0 and 1.
Consequently, we chose a different way of quantifying the individual degree of ED.
A classic AUC cannot differentiate between a subject who prefers 1-back and a subject who prefers 4-back, but can reflect the overall willingness to exert effort.
This is the opposite for the sum of the ascent between SVs.
Therefore, we multiply both indicators, arriving at a value reflecting both degree and direction of preference, called $AxAUC$.

##Power analysis
A sample size analysis with GPower [@Faul2007; @Faul2009], using the pilot RT data, indicated that we should collect data from at least 40 participants, assuming $f=0.27$, $\alpha=.05$, $\beta=.80$, and no correlation between levels.

@@

### Associations of subjective and objective task load measures
Contrary to our expectations, the rmANOVA revealed no decrease in performance *d'* with increasing n-back level (`r apa_print(hypothesis1a_rmanova)$full_result`).

@@

However, RT increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
RTs were longer for 3- than 2-back (`r apa_print(hypothesis1b_contrasts)$statistic[1]`), but not different between 2- and 4-back or 3- and 4-back.
Even though *d'* did not decrease, the increases in RT indicate an increase in objective task load.

@@

Increases in subjective task load were investigated for each NASA-TLX subscale, now including 1-back.
Ratings on the mental load and effort subscales increased between all n-back levels ($p<.001$) except between 3- and 4-back.
Ratings on the physical load and the performance subscales only increased between 1- and 3-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X3`, and `r `apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X3`, respectively) and 1- and 4-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X4`, and `r `apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X4`, respectively).
Ratings on the frustration and time pressure subscales increased between all n-back levels ($p<.001$) except between 1- and 2-back and 3- and 4-back.
Overall, these ratings showed that the increase in task load was being perceived as such.

@@

### Changes in subjective values depending on n-back level
The rmANOVA indicated significant differences between SVs depending on n-back level (`r apa_print(hypothesis2a_rmanova)$full_result`).
SVs were higher for 1- than 3-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X3`), for 1- than 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X4`), and for 2- than 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X2_X4`).
The lack of difference between the SVs of 1- and 2-back indicates that when given the choice, not all participants preferred the easiest level.

@@

When including the AUC of all NASA-TLX subscales as a predictor, it could explain variance in NFC beyond the one (not) explained by the SVs (`r apa_print(hypothesis3b)$statistic$modelfit$r2`, `r apa_print(hypothesis3b)$estimate$modelfit$r2`).
An increase in one NASA_NTLX AUC value corresponded, on average, to a decrease of `r round(hypothesis3b$coefficients[2], digits = 1)` on the NFC scale (`r apa_print(hypothesis3b)$estimate$h3_data_auc_ntlx`).

>>>>

---
title             : "When easy is not preferred: The Cognitive and Emotion Regulation Effort Discounting paradigm (CERED) for estimating subjective values of cognitive tasks"
shorttitle        : "The CERED paradigm for estimating subjective values"
author: 
  - name          : "Josephine Zerna"
    affiliation   : "1,*"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    affiliation   : "1,*"
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
  * Shared first authorship
abstract: |
  Every day, individuals have to weigh the value of the reward when reaching a goal against the required effort.
  However, effort is not inherently aversive to all individuals, which has often been neglected by previous approaches to quantify the subjective value of effort.
  One of them is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013), which can quantify the subjective values of the difficult levels of the n-back task against the easiest level.
  We aim to replicate the analysis of Westbrook et al. (2013) with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm (CERED).
  The CERED paradigm will likely enable a more insightful investigation of interindividual differences in effort discounting, as well as the investigation of effort discounting for task types for which this is currently not possible due to their high degree of subjectivity.

  We argue that adapting the paradigm and the method of computing the willingness to exert effort allows two crucial things: Quantifying subjective values without assuming that the easiest level is preferred, and quantifying subjective values for tasks with no objective order of task load.
keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "X"
bibliography      : ref_COG-ED.bib
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : apa.csl # this is a workaround for a current bug in the papaja/Rmd software, which fails to shorten multiple authors to "et al."
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
editor_options: 
  markdown: 
    wrap: sentence
---

@@

@@

In everyday life, effort and reward are closely intertwined [@Botvinick2009].
With each decision a person makes, they have to evaluate whether the effort required to reach a goal is worth being exerted, given the reward they receive when reaching the goal.
A reward is subjectively more valuable if it is obtained with less effort, so the required effort is used as a reference point for estimating the reward value [@Botvinick2009].
However, the cost of the effort itself is also subjective, and research has not yet established which function best describes the relationship between effort and cost [@Kool2018].
Investigating effort and cost is challenging because "effort is not a property of the target task alone, but also a function of the individual's cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual's reward sensitivity" [@Kool2018, p. 209].

## Effort discounting and Need for Cognition

The individual degree of ED in the study by Westbrook et al. [-@Westbrook2013] was also associated with the participants' Need for Cognition (NFC) score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
Westbrook et al. [-@Westbrook2013] conceptualized NFC as a trait measure of effortful task engagement, providing a subjective self-report of ED for each participant which could then be related to the SVs as an objective measure of ED.
On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
Additionally, it has been shown that individuals avoid cognitive effort only to a certain degree, possibly to retain a sense of self-control [@Wu2021], a trait more prominent in individuals with high NFC [@Bertrams2012; @Nishiguchi2016; Xu2021].
However, the relation of NFC and SVs might be confounded, since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance [@Kramer2021] or found no association of NFC and SVs at all [@Crawford2021].
On the other hand, task load has been shown to be a better predictor of SVs than task performance [@Culbreth2016; @Westbrook2013; @Westbrook2019], so more research is needed to shed light on this issue.

## Revising the COG-ED paradigm

The present study changes one fundamental assumption of the original COG-ED paradigm: That the easiest n-back level has the highest SV.
We adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different n-back levels without presuming that all individuals inherently prefer the easiest level.
Figure 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
The COG-ED paradigm sets the SV of 1-back to 1, regardless of the response pattern.
Adding a comparison of 2-back and 3-back allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
Adding three more comparisons of the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
First, the SVs are still distorted by the SVs returned by the original paradigm, and second, having more task levels would lead to an exponential increase in comparisons.
Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one ED round for each possible pair of levels, and by starting each round with a choice between equal prices.
For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
The level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
The level that was not chosen will be set to a fixed value of 2€.
This procedure allows to compute SVs based on actual individual preference instead of objective task load.
Each level's SV is calculated as the mean of this level's SVs from all comparisons in which it appeared.
If the participant has a clear preference for one level, this level's SV will be 1.
If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's ED behaviour can still be quantified.
Since we aim to establish this paradigm for the assessment of tasks with no objective task load, e.g. emotion regulation tasks, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013]. Additionally, we will compare the ED behaviour of participants regarding the n-back task and an emotion regulation task. The full results of the latter will be published in a second Registered Report. The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for emotion regulation.

*Fig.1* Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.

## Hypotheses

Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
Regarding the associations of subjective and objective task load we hypothesize that (1a) performance measured by signal detection *d'* declines with increasing n-back level, (1b) performance measured by reaction time declines with increasing n-back level, and (1c) perceived task load increases with n-back level.
Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.

@@

The paradigm was written and presented using *Psychopy* [@Peirce2019]. We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
The R Markdown file used to analyze the data and write this document is freely available at github.com/ChScheffel/CERED.
The data can be downloaded from osf.io/vnj8x/.

## Questionnaires

To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
NFC will be assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
Responses to each item (e.g., "Thinking is not my idea of fun", recoded) will be recorded on a 7-point Likert scale.
The NFC scale shows comparably high internal consistency [Cronbach's $\alpha$ \> .80; @Bless1994; @Fleischhauer2010].
Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session.
A full list of measures can be found at osf.io/vnj8x/.

## Procedure

Healthy participants aged 18 to 30 years will be recruited using the software *ORSEE* [@Greiner2015]. Participants will fill out the personality questionnaires online and then visit the lab for two sessions one week apart. In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm. The paradigm starts with the n-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run. The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure. After each level, participants fill out the NASA-TLX on a tablet. Then, they complete the ED procedure on screen, where each possible pairing of the four n-back levels is presented in a randomized order. Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of n-back. This is only done to incentivise truthful behavior in the ED procedure, so the n-back data of this part will not be analyzed. The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively. The paradigm follows the same structure of task and ED procedure, but participants can decide which strategy they want to reapply in the last block. Participants will receive 30€ in total or course credit for participation. Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
The sample of the pilot study consisted of $N=$ `r length(datalist_ED)` participants (`r round((table(data_quest$gender)[2]/length(datalist_ED))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
In the pilot study, the online questionnaires were completed after the two lab sessions, but we will change this as described above, so that the participants do not have to come in again to collect their money or course credit.

## Analysis

We aim to conduct all analysis as described in Westbrook et al. [-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom. The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990]. Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021]. Error- and post-error trials will be excluded, because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
Declining performance will be investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
For each ED round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
A rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Tukey method will be used for the paired contrasts of each rmANOVA, including *p*-value adjustment.

To determine the influence of task performance in the association of SVs and n-back level, we will set up a multi-level model.
**MLM explanation goes here** To ensure the validity of the multi-level model, we will conduct a specification curve analysis [@Simonsohn2020], which will include 92 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, $2 SD$ from the mean, $3 SD$ from the mean, RTs below 200 ms), whether post-error trials were excluded or not, and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
The multi-level model will be run with each of the 92 pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 200 ms, removal of post-error trials).
The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.

The association of ED and NFC will be examined with a regression using the AUC of each participant's SVs to predict their NFC score.
A second regression will additionally include the mean of the NASA-TLX subscales' AUCs of each participant as a predictor.
Since we do not have a fixed SV of 1 for 1-back, we cannot apply the "AUC" computation of Westbrook et al. [-@Westbrook2013], which was the mean of the AUCs of the SVs of each higher n-back level and 1-back, yielding values between 0 and 1.
Consequently, we chose a different way of quantifying the individual degree of ED.
A classic AUC cannot differentiate between a subject who prefers 1-back and a subject who prefers 4-back if the magnitude of the ascent is the same, but it can reflect the overall willingness to exert effort.
This is the opposite for the sum of the ascent between SVs.
Therefore, we multiply both indicators, arriving at a value reflecting both degree and direction of preference, called $AxAUC$.

## Power analysis

A sample size analysis with GPower [@Faul2007; @Faul2009], using the pilot RT data, indicated that we should collect data from at least 40 participants, assuming $f=0.27$, $\alpha=.05$, $\beta=.80$, and no correlation between levels.

@@

### Associations of subjective and objective task load measures

Contrary to our expectations, the rmANOVA revealed no decrease in performance *d'* with increasing n-back level (`r apa_print(hypothesis1a_rmanova)$full_result`).

@@

However, RTs increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
RTs were longer for 3- than 2-back (`r apa_print(hypothesis1b_contrasts)$statistic[1]`), but not different between 2- and 4-back or 3- and 4-back.
Even though *d'* did not decrease, the increases in RT indicate an increase in objective task load.

@@

Increases in subjective task load were investigated for each NASA-TLX subscale, now including 1-back.
Ratings on the mental load and effort subscales increased between all n-back levels ($p<.001$) except between 3- and 4-back.
Ratings on the physical load and the performance subscales only increased between 1- and 3-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X3`, and `r`apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X3`, respectively) and 1- and 4-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X4`, and`r `apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X4`, respectively).
Ratings on the frustration and time pressure subscales increased between all n-back levels ($p<.001$) except between 1- and 2-back and 3- and 4-back.
Overall, these ratings showed that the increase in task load was being perceived as such.

@@

### Changes in subjective values depending on n-back level

The rmANOVA indicated significant differences between SVs depending on n-back level (`r apa_print(hypothesis2a_rmanova)$full_result`).
SVs were higher for 1- than 3-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X3`), for 1- than 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X4`), and for 2- than 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X2_X4`).
Importantly, the lack of difference between the SVs of 1- and 2-back indicates that when given the choice, not all participants preferred the easiest level.
This can be considered preliminary proof-of-concept, as this behavioural pattern can only emerge in the CERED paradigm, but not in the original COG-ED paradigm.

@@

When including the AUC of all NASA-TLX subscales as a predictor, it could explain variance in NFC beyond the one (not) explained by the SVs (`r apa_print(hypothesis3b)$statistic$modelfit$r2`, `r apa_print(hypothesis3b)$estimate$modelfit$r2`).
An increase in one NASA-TLX AUC value corresponded, on average, to a decrease of `r round(hypothesis3b$coefficients[2], digits = 1)` on the NFC scale (`r apa_print(hypothesis3b)$estimate$h3_data_auc_ntlx`).

\newpage

# Acknowledgements

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

\endgroup
